Embedding Intuitionistic into Classical Logic

### 2022-10-14 FoSSaCS/fossacs-EIICL.tex
incoprporated notes

We further mention some translations between logics from the literature.
Most relevant are the embedding of intuitionistic logic into S4~\cite{basicprooftheory} and of various non-classical logics into higher-order classical logic~\cite{LEO,wisniewski2016tptp} \todo{why are they relevant?}.
Of special relevance is the reduction of intuitionistic propositional logic given in~\cite{claessen2015sat}
\todo{reduction to what?} and examined in~\cite{fiorentini2019proof} \todo{what has been examined here?}, which we further expand upon in this paper.

\todo{This paragraph is more about realizability, right? So remove, or connect to paper?}
On the other hand there have been attempts to circumvent intuitionistic logic by equipping classical proofs with operational semantics~\cite{Control1,Parigot1}, which however does not permit in general the realizability of $\exists$ and $\vee$.

@@

Two versions of the translation were tested, one with and one without the additional axioms encoding idempotence. The results are stated in Figure \ref{fig:a}. 
In general, our approach falls short of the state of the art. 
However when grouping the benchmarks by $|\mathcal Q|$ and $|\mathcal X|$, see Figure~\ref{fig:b},
we observe good performance of our approach for $|\mathcal Q| = 0$ and $|\mathcal X| \leq 2$ resp. $|\mathcal X| \geq 6$.
\todo{Note that I added $\ge 6$.}
Figure~\ref{fig:c} shows that our approach solved 52 problems not solved by the state-of-the-art provers.
\begin{figure}
	\centering
	\begin{tabular}{c|c|lr|lr|lr|lr|c}
		$|\mathcal Q|$&$|\mathcal X|$&\multicolumn{2}{c}{Embedding}&\multicolumn{2}{c}{Embedding (idem.)}&\multicolumn{2}{c}{ileanCoP}&\multicolumn{2}{c}{nanoCoP-i 2.0}&Total\\\hline
		0&0		&157&88.2\%	&157&88.2\%		&128&71.9\%		&61&38.1\%	&178\\
		0&1-2	&119&29.8\%&130&32.5\%		&108&27.0\%		&96&24.0\%	&400\\
		0&3-5	&16&15.2\%	&17&16.2\%		&50&47.6\%		&40&28.1\%	&105\\
		0&6+	&27&38.6\%	&11&15.7\%		&20&28.6\%		&11&15.7\%	&70\\
		1-2&0-2	&84&29.3\%	&81&28.2\%		&227&79.1\%		&221&77.0\%	&287\\
		1-2&3-5	&80&25.6\%	&77&24.7\%		&141&45.2\%		&122&39.1\%	&312\\
		1-2&6+	&22&21.8\%	&21&20.8\%		&39&38.6\%		&37&36.6\%	&101\\
		3-5&0-5	&38&17.0\%	&40&17.9\%		&125&55.8\%		&110&49.1\%	&224\\
		3-5&6+  &20&8.4\%	&18&7.6\%		&64&27.0\%		&86&36.3\%	&237\\
		6+&0+	&8&1.1\%	&5&0.7\%		&73&9.7\%		&74&9.8\%	&755
	\end{tabular}
	\caption{Solved problems grouped by $|\mathcal Q|$ and $|\mathcal X|$.}
	\label{fig:b}
\end{figure}

>>>>

We further mention some translations between logics from the literature.
Most relevant are the embedding of intuitionistic logic into S4~\cite{basicprooftheory} and of various non-classical logics into higher-order classical logic~\cite{LEO,wisniewski2016tptp}.
Of special relevance are the normalization procedures for intuitionistic propositional logic given in~\cite{claessen2015sat}
and examined from a proof-theoretic perspective in~\cite{fiorentini2019proof}, which we further expand upon in this paper.

@@

Two versions of the translation were tested, one with and one without the additional axioms encoding idempotence. The results are stated in Figure \ref{fig:a}. 
In general, our approach falls short of the state of the art. 
However when grouping the benchmarks by $|\mathcal Q|$ and $|\mathcal X|$, see Figure~\ref{fig:b},
we observe good performance of our approach for $|\mathcal Q| = 0$ and $|\mathcal X| \leq 2$ resp. $|\mathcal X| \geq 6$.
Figure~\ref{fig:c} shows that our approach solved 52 problems not solved by the state-of-the-art provers.\pagebreak
\begin{figure}
	\centering
	\begin{tabular}{c|c|lr|lr|lr|lr|c}
		$|\mathcal Q|$&$|\mathcal X|$&\multicolumn{2}{c}{Embedding}&\multicolumn{2}{c}{Embedding (idem.)}&\multicolumn{2}{c}{ileanCoP}&\multicolumn{2}{c}{nanoCoP-i 2.0}&Total\\\hline
		0&0		&157&88.2\%	&157&88.2\%		&128&71.9\%		&61&38.1\%	&178\\
		0&1-2	&119&29.8\%&130&32.5\%		&108&27.0\%		&96&24.0\%	&400\\
		0&3-5	&16&15.2\%	&17&16.2\%		&50&47.6\%		&40&28.1\%	&105\\
		0&6+	&27&38.6\%	&11&15.7\%		&20&28.6\%		&11&15.7\%	&70\\
		1-2&0-2	&84&29.3\%	&81&28.2\%		&227&79.1\%		&221&77.0\%	&287\\
		1-2&3-5	&80&25.6\%	&77&24.7\%		&141&45.2\%		&122&39.1\%	&312\\
		1-2&6+	&22&21.8\%	&21&20.8\%		&39&38.6\%		&37&36.6\%	&101\\
		3-5&0-5	&38&17.0\%	&40&17.9\%		&125&55.8\%		&110&49.1\%	&224\\
		3-5&6+  &20&8.4\%	&18&7.6\%		&64&27.0\%		&86&36.3\%	&237\\
		6+&0+	&8&1.1\%	&5&0.7\%		&73&9.7\%		&74&9.8\%	&755
	\end{tabular}
	\caption{Solved problems grouped by $|\mathcal Q|$ and $|\mathcal X|$.}
	\label{fig:b}
\end{figure}
\vspace*{-.5cm}
